Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-11-09 prob.tex
prob.tex \section{Proofs} Conjecture is false. So... How to fix it?

\begin{definition}\cite{gleason1957,CookeKeaneMoran1985,RichmanBridges1999,Hamhalter2013}~Given
a vector~$\ket{\psi}\in S^{2}$ with a specified north pole~$\ket{0}\in S^{2}$,
then 
\begin{itemize}
\item $\theta\left(\ket{\psi}\right)=\arccos\ip{0}{\psi}$ denotes the the
latitude of $\ket{\psi}$.
\item The great circle on $S^{2}$ is the intersection of $S^{2}$ with
a plane containing the center of $S^{2}$.
\item If $0<\theta\left(\ket{\psi}\right)<\frac{\pi}{2}$, there is a unique
great circle tangent to the circle of latitude through $\ket{\psi}$;
we shall call it East-West great circle through $\ket{\psi}$, and
denoted by $C\left(\ket{\psi}\right)$.
\end{itemize}
\qed\end{definition}

\yutsung{\begin{lemma}\label{lemma:geometricInterludeRichmanBridges1999}\cite{RichmanBridges1999}~Let
$\ket{\psi}$ and $\ket{\psi'}$ be points in $N_{\ket{0}}$ with
the latitude~$\theta\left(\ket{\psi}\right)=\theta\left(\ket{\psi'}\right)$.
Then there exist a finite number~$n\ge\frac{a^{2}}{\theta\left(\ket{\psi}\right)}$
steps along east-west great circles to go from $\ket{\psi'}$ to a
point $\ket{\psi_{s}}$ due south of $\ket{\psi}$.\footnote{Verify the details more precisely...}\qed\end{lemma}

@@

\begin{conjecture}\label{conj:analogGeometricInterludeRichmanBridges1999}There
exist a nonempty set~$\mathcal{N}\subseteq\mathbb{N}\cap\left[2\pi,\infty\right)$
such that for all $n\in\mathcal{N}$, if $\ket{\psi}$ and $\ket{\psi'}$
are points in the northern hemisphere with the latitude~$\theta\left(\ket{\psi}\right)=\theta\left(\ket{\psi'}\right)$,
then we could takes $n$ steps along east-west great circles to go
from $\ket{\psi'}$ to a point $\ket{\psi_{s}}$ due south of $\ket{\psi}$.\footnote{Verify the details more precisely...}\qed\end{conjecture}

>>>>

\begin{definition}\cite{gleason1957,CookeKeaneMoran1985,RichmanBridges1999,Hamhalter2013}~Given
a vector~$\ket{\psi}\in S^{2}$ with a specified north pole~$\ket{0}\in S^{2}$,
then 
\begin{itemize}
\item $\theta\left(\ket{\psi}\right)=\arccos\ip{0}{\psi}$ denotes the the
latitude of $\ket{\psi}$.
\item The great circle on $S^{2}$ is the intersection of $S^{2}$ with
a plane containing the center of $S^{2}$.
\item If $0<\theta\left(\ket{\psi}\right)<\frac{\pi}{2}$, there is a unique
great circle tangent to the circle of latitude through $\ket{\psi}$;
we shall call it a East-West great circle through $\ket{\psi}$, and
denoted by $C\left(\ket{\psi}\right)$.
\item A point~$\ket{\psi'}$ in a East-West great circle~$C\left(\ket{\psi}\right)$
is \emph{close to} $\ket{\psi}$ if 
\[
\cos\theta\left(\ket{\psi'}\right)=\ip{0}{\psi'}\le2\ip{0}{\psi}=2\cos\theta\left(\ket{\psi}\right)\textrm{ .}
\]
\end{itemize}
\qed\end{definition}

\yutsung{\begin{lemma}\label{lemma:geometricInterludeRichmanBridges1999}\cite{RichmanBridges1999}~Let
$\ket{\psi}$ and $\ket{\psi'}$ be points in the northern hemisphere
with the latitude~$\theta\left(\ket{\psi}\right)=\theta\left(\ket{\psi'}\right)$.
Then, we can take a finite number~$n$ close steps along East-West
great circles to go from $\ket{\psi'}$ to a point $\ket{\psi_{s}}$
due south of $\ket{\psi}$.\qed\end{lemma}

@@

\begin{conjecture}\label{conj:analogGeometricInterludeRichmanBridges1999}There
exist a nonempty set~$\mathcal{N}\subseteq\mathbb{N}\cap\left[2\pi,\infty\right)$
such that for all $n\in\mathcal{N}$, if $\ket{\psi}$ and $\ket{\psi'}$
are points in the northern hemisphere with the latitude~$\theta\left(\ket{\psi}\right)=\theta\left(\ket{\psi'}\right)$,
then we could takes $n$ close steps along east-west great circles
to go from $\ket{\psi'}$ to a point $\ket{\psi_{s}}$ due south of
$\ket{\psi}$.\qed\end{conjecture}
